The ChEMBL database as Linked Open Data

### 2013-03-26 article.tex
fix reviewer 1 comment 5 to change from 1.3 million to 1.1 million
add school for my affiliation

\address{\iid(1)Department of Bioinformatics - BiGCaT, Maastricht University, P.O. Box 616, UNS50 Box 19, NL-6200 MD, Maastricht, The Netherlands  \\
\iid(2)Department of Pharmaceutical Biosciences, Uppsala University, PO Box 591, SE-751 24, Uppsala, Sweden \\
\iid(3)University of Queensland, St Lucia, Qld 4072, Australia \\
\iid(4)Royal Society of Chemistry, 904 Tamaras Circle, Wake Forest, NC 27587, U.S.A. \\
\iid(5)Cheminformatics and Metabolism, European Bioinformatics Institute, Wellcome Trust Genome Campus, Hinxton, Cambridgeshire, CB10 1SD, United Kingdom \\
\iid(6)Chemogenomics, European Bioinformatics Institute, Wellcome Trust Genome Campus, Hinxton, Cambridgeshire, CB10 1SD, United Kingdom \\ 
\iid(7)School of Informatics and Computing, Indiana University, Bloomington, IN, U.S.A.
}

@@

The InChI is a unique identifier for (small) organic molecules, and has been previously used
to define unique URIs for molecules~\cite{Bradley2009,Willighagen2011}. While URIs are theoretically unlimited in length,
in practice many web browsers and servers limit the length of URIs. Virtuoso is, unfortunately,
one such system that supports only URIs of up to a certain length. Therefore, InChI-based links are only created for smaller molecules. 
Almost 1.3 million links to OpenMolecules RDF were created in a similar manner to:

>>>>

\address{\iid(1)Department of Bioinformatics - BiGCaT, Maastricht University, P.O. Box 616, UNS50 Box 19, NL-6200 MD, Maastricht, The Netherlands  \\
\iid(2)Department of Pharmaceutical Biosciences, Uppsala University, PO Box 591, SE-751 24, Uppsala, Sweden \\
\iid(3)School of Information Technology and Electronic Engineering, University of Queensland, St Lucia, Qld 4072, Australia \\
\iid(4)Royal Society of Chemistry, 904 Tamaras Circle, Wake Forest, NC 27587, U.S.A. \\
\iid(5)Cheminformatics and Metabolism, European Bioinformatics Institute, Wellcome Trust Genome Campus, Hinxton, Cambridgeshire, CB10 1SD, United Kingdom \\
\iid(6)Chemogenomics, European Bioinformatics Institute, Wellcome Trust Genome Campus, Hinxton, Cambridgeshire, CB10 1SD, United Kingdom \\ 
\iid(7)School of Informatics and Computing, Indiana University, Bloomington, IN, U.S.A.
}

@@

The InChI is a unique identifier for (small) organic molecules, and has been previously used
to define unique URIs for molecules~\cite{Bradley2009,Willighagen2011}. While URIs are theoretically unlimited in length,
in practice many web browsers and servers limit the length of URIs. Virtuoso is, unfortunately,
one such system that supports only URIs of up to a certain length. Therefore, InChI-based links are only created for smaller molecules. 
Almost 1.1 million links to OpenMolecules RDF were created in a similar manner to:
